Evaluation of Types

### 2020-05-15 evaluation/R/evaluate-type-analysis.Rmd

>>>>

##

```{r, eval = TRUE, verbose = FALSE}
union_frequency <-
union_data %>%
distinct(package_name, function_name, parameter_position) %>%
mutate(polymorphic = ifelse(alternative_count > 1, true, is_polymorphic(alternative_count)) %>%
group_by(package_name, function_name, polymorphic_position_count = )
group_by(alternative_count) %>%
summarize(parameter_count = n()) %>%
ungroup() %>%
arrange(desc(parameter_count)) %>%
mutate(percentage = round(parameter_count / sum(parameter_count), 4),
       cumulative_percentage = round(cumsum(parameter_count) / sum(parameter_count), 4))
```
